\documentclass[english]{article}

\usepackage{babel}
\usepackage{graphicx}
\usepackage{times}
\usepackage{pifont}
\usepackage[margin=0.9in]{geometry}
\usepackage{eurosym}
\usepackage{fancyhdr}
\usepackage[hidelinks]{hyperref}
\pagestyle{fancy}
\fancyhf{}


%HEADER
%**************************************************************************************
\pagestyle{fancy}
\fancyhf{}
%**************************************************************************************
\lhead{Cover Letter}
\rhead{\today}		 	 
%**************************************************************************************

\date{}
\setlength\parindent{0pt}

\begin{document}

\begin{flushright}
Alexey Tukalo,\\
airtucha@icloud.com,\\
Taivaanpankontie 14 A 14/1,\\
70200 Kuopio, Finland
\end{flushright}

Dear Madam, Sir,\\ 

Graduating from Bachelor of Information Technology I am looking for an opportunity to get some real life experience in one of the most respectable companies in the world. With this letter I hereby wish to state my interest and apply for a JavaScript Developer Internship programme in Opera Software.\\

Relocation is not trouble for me, I have a sufficient experience of studying and working abroad. I was born in a small town located on the seashore of the White Sea at North West part of Russia. My hometown is very small, so I had to leave it to continue my education. Almost four years ago, when I was eighteen years old I moved abroad to get the world-class education.\\

Moreover, I took a part in an Erasmus+ Exchange programme in Ireland for one semester, there I made my first more or less serious project with JavaScript, it was an interactive visualisation\footnote{I used D3.js for a very simple front-end, MongoDB database and Express Node.js as back-end} for a prototype of a garbage monitoring system. It is worth mentioning that my hobby is a landscape, street and portrait photography\footnote{You can find my photos here - 500px.com/alexeytukalo}, I brought a lot of photos from the trip. The irish nature was very unusual for me, because my homeland is very flat, so this travel opened the beauty of mountains for me and I hope I would be able to take some nice pictures in Norway, your Fjords are even higher.\\

Right after that I was hired by Karlsruhe Institute of Technology as an intern where I worked at Institute of Data Processing and Electronics for more than 4 months. The project was related with development of a device for an early diagnostics of the breast cancer, they were able to produce three different types of images and I had to find the solution to fuse them into single one in convenient way. The most part of the work placement I did image processing with Java, but I also developed promo website for the project based on WebGL implementation of my algorithm integrated into the volume rendering library developed by KIT\footnote{ipepc57.ipe.kit.edu:10002}. The algorithm is used in a clinical studies and I am mentioned as co-author of an article published in a peer review journal about medicine.\\

The experience of data visualisation and digital image processing gained in Germany has contributed to get a part-time job at Arction Oy, Finland. Right now, I am doing a my final thesis project in collaboration with this company\footnote{Implementation of volume rendering in LightningChart}. At the moment, I work on a development of LightningChart\footnote{The fastest C\# framework for visualisation of scientific data}. I am also going to make promo website\footnote{ReactJS front-end and Express Node.js back-end} for one of our new products.\\

In my point of view every person which I meet during my life can teach me something useful. This internship is an amazing chance to meet a lot of people with totally different cultural backgrounds, lifestyles and habits. So, I think that it is a great opportunity to spread the network of acquaintances and absorb some new ideas.\\

%Ending
Please, consider me as a potential candidate to the internship programme. I am excited by an opportunity to have a chance to be a part of Opera team at least for a while. In my point of view such a huge brands have their own internal culture and it would be interesting for me to make myself familiar with yours. In the end, I want to notice that I really love JavaScript and I am very happy to have a chance to learn something from such a professionals as your team. It would mean a lot for my future career prospects in Opera or anywhere else. \\\\


Thank you in advance.\\
Yours faithfully,\\
Alexey Tukalo
    

\end{document}
