\documentclass[english]{article}

\usepackage{babel}
\usepackage{graphicx}
\usepackage{times}
\usepackage{pifont}
\usepackage[margin=1in]{geometry}
\usepackage{eurosym}
\usepackage{fancyhdr}
\usepackage[hidelinks]{hyperref}

\pagestyle{fancy}
\fancyhf{}


%HEADER
%**************************************************************************************
\pagestyle{fancy}
\fancyhf{}
%**************************************************************************************
\lhead{ICT Services and R\&D}		 	 
\rhead{Second home work} 
\lfoot{EFA12SF}
\rfoot{Alexey Tukalo}
%**************************************************************************************

\date{}
\setlength\parindent{0pt}

\begin{document}
ICT services are provided by many famous companies like: Microsoft, Oracle, IBM, Apple, Xerox, Yahoo, Adobe, AT\&T, Verizon, Tele2, DNA, Nokia, Alphabet, Amazon, Red Hat and so on. The companies are specialised in different areas and provide a various number of services like: cable or mobile internet connections, clouds storage, cloud computing(PaaS, SaaS), different types of APIs, searching engines, hosting, e-commerce, web/desktop/mobile applications and many many other things. The head offices of the most part of the companies are located on the west seashore of the USA, but they have R\&D center whole over the world. The core part of the companies` staff are computer scientists, software engineers, system administrators, specialists in electronics and board design. The typical ICT company is relativity young the most part of them is found during last 10-30 years, but there are also several companies which are much older than the entire ICT industry and their initial fields were not related with this kind of technology.\\

I think I can make career at this type of companies, because they are doing a lot of different stuff and the most part of this things are related with my curriculum and skills. I am especially interested in web development, data analysing and visualisation. So, I can be useful on building of GUI for different types of servers or in development of the product related with data analysing for example recommendations or targeted advertising. I also can make career as growth hacker in young ICT company.

\end{document}
