\documentclass[english]{article}

\usepackage{babel}
\usepackage{graphicx}
\usepackage{times}
\usepackage{pifont}
\usepackage[margin=1in]{geometry}
\usepackage{eurosym}
\usepackage{fancyhdr}
\usepackage[hidelinks]{hyperref}
\pagestyle{fancy}
\fancyhf{}


%HEADER
%**************************************************************************************
\pagestyle{fancy}
\fancyhf{}
%**************************************************************************************
\lhead{Cover Letter}
\rhead{\today}		 	 
%**************************************************************************************

\date{}
\setlength\parindent{0pt}

\begin{document}

\begin{flushright}
Alexey Tukalo,\\
airtucha@icloud.com,\\
Taivaanpankontie 14 A 14/1,\\
70200 Kuopio, Finland
\end{flushright}

Dear Madam, Sir,\\ 

Graduating from Bachelor of Information Technology I am looking for an opportunity to continue my education at Master level from the next Autumn. With this letter I hereby wish to state my interest and apply for Erasmus Mundus Joint Master Degree (EMJMD) programme in Colour in Science and Indastry.\\

In my opinion, this kind of travel can be an interesting challenge. However, I am sure I am able to handle it, since I have a sufficient experience of studying and working abroad. In addition, I am very impressed by the mobility structure of the programm, it seems to be it is an amazing chance to meet a lot of people with totally different cultural backgrounds, lifestyles and habits. In my point of view every person which I meet during my life can teach me something useful. So, I think that it is a great opportunity to spread the network of acquaintances and to absorb some of habits and customs of the host nations. It is worth mentioning that my hobby is a landscape, street and portrait photography\footnote{500px.com/alexeytukalo}, that’s why I am especially impressed by the program, it would give me a possibility to take a large number of photos of new people from a various number of places around Europe. I think that the expirince in visual art and understanding of computer science give me an opportunity to reach quite good results for amature.\\

My passion to the visual art started in chilhood when I went to the art school, at that time I used to dream to became an arcitecture, indastial designer or web-designer later. But I am also very good at Math and Computer Science, that was the reason of applying for Bachelor Degree in Information Technology in Finland with tuition in English. Moreover, I took a part in an Erasmus+ Exchange programme in Ireland for one semester. I always tried to combine my interest to the visual art with my knowledge on computer scince, in Ireland I got my first expirince in data visualisation amd I found perfect balance between the fields there.\\

Right that I was hired by Karlsruhe Institute of Technology as an intern where I worked at Institute of Data Processing and Electronics for more than 4 months\footnote{Reference from Dr. Hopp}. The project was related with development of a device for an early diagnostics of the breast cancer. The most part of the work placement I did image processing with Java. The visual expirince and knowledge of colour models learned from photography helped me a lot. I also developed promo website for the project based on WebGL implementation of my algorithm integrated into the volume rendering library developed by KIT\footnote{ipepc57.ipe.kit.edu:10002}. The algorithm is used in a clinical studies and I am mentioned as co-author of an article published in a peer review journal about medicine. The experience of data visualisation and digital image processing gained in Germany has contributed to get a job at Arction Oy, Finland. I am also doing a my final thesis project in collaboration with this company\footnote{Implementation of volume rendering in LightningChart, the fastest C\# framework for visualisation of scientific data}. As you can see the most part of my profesional expirince is related with medical image processing and visualisation of medical data, so obviousely the profelisation in Applied Colour Imaging is the most suitable for me.\\

Besides, my knowledge in computer scince and visual art I am well orgonised persone, I really like to organise my own work and work of my teammates. I am always trying to improve my leadership skills and gain an expirince in project management, it was the main reasone why I joined Pricelizer team\footnote{Reference from Karl Lillrud}. In Pricelizer I got a lot of expirince in terms of project management of IT project for team distributed around the worled.\\

%Ending
Please, consider me as a potential candidate to Erasmus Mundus Joint Master Degree (EMJMD) programme in Colour in Science ans Indastry and Erasmus+ Joint Master Degree scholarship. I beleive that this programme will have a great value in my career prospects. This experience will be a huge motivation for me to bring new ideas to the industry. \\\\


Thank you in advance.\\
Yours faithfully,\\
Alexey Tukalo
    

\end{document}
