\documentclass[english]{article}

\usepackage{babel}
\usepackage{graphicx}
\usepackage{times}
\usepackage{pifont}
\usepackage[margin=1in]{geometry}
\usepackage{eurosym}
\usepackage{fancyhdr}
\usepackage[hidelinks]{hyperref}
\pagestyle{fancy}
\fancyhf{}


%HEADER
%**************************************************************************************
\pagestyle{fancy}
\fancyhf{}
%**************************************************************************************
\lhead{Motivation Letter}
\rhead{\today}		 	 
%**************************************************************************************

\date{}
\setlength\parindent{0pt}

\begin{document}

\begin{flushright}
Alexey Tukalo,\\
airtucha@icloud.com,\\
Taivaanpankontie 14 A 14/1,\\
70200 Kuopio, Finland
\end{flushright}

Dear Madam, Sir,\\ 

Graduating from Bachelor of Information Technology I am looking for an opportunity to continue my education at Master level from the next Autumn. With this letter I hereby wish to state my interest and apply for Erasmus Mundus Joint Master Degree (EMJMD) programme in Mathematical Modelling in Engineering.\\

My passion to Math started at school. There I was inspired to pay a lot of extra care to the subject and as a result, I got the highest grade at the final exam of Math in the history of my school. That was the reason of applying for Bachelor Degree in Information Technology in Finland. Savonia University of Applied Science provided me with an opportunity to improve my mathematical background as well as helped me to get a deep understanding of programming.\\

I believe that a studying at MathMods will help me to evolve my mathematical abilities to the next level. I am very impressed by the mobility structure of the programm, because it is an amazing chance to meet a lot of people with totally different cultural backgrounds, lifestyles and habits. In my point of view every person which I meet during my life can teach me something useful. So, I think that it is a great opportunity to spread the network of acquaintances and to absorb some of habits and customs of the host nations.\\

It is worth mentioning that my hobby is a landscape, street and portrait photography\footnote{500px.com/alexeytukalo}, that’s why I am especially impressed by the program, it would give me a possibility to take a large number of photos of new people from a various number of places around Europe.\\

In my opinion, this kind of travel can be an interesting challenge. However, I am sure I am able to handle it, since I have a sufficient experience of studying and working abroad. I was born in a small town located on the seashore of the White Sea at North West part of Russia. My hometown is very small, so I had to leave it to continue my education. Almost four years ago, when I was eighteen years old I moved abroad to get the world-class education.\\

Moreover, I took part in an Erasmus+ Exchange programm in Ireland for one semester. I would like to notice that this experience opened the world of data science for me and partly changed my point of view on my future career. Data analysis has wide range of applications, especially in economics. That is why Mathematical Modelling Applications to Finance is the most interesting specialisation of MathModes for me.\\

Right after that I was hired by Karlsruhe Institute of Technology as an intern where I worked at Institute of Data Processing and Electronics for more than 4 months. The experience of data visualisation and digital image processing gained in Germany has contributed to get a part time job at Arction Oy, Finland. Furthermore, I made a decision to base my final thesis project in collaboration with this company\footnote{Implementation of volume rendering in LightningChart}. At the moment, I work on development of LightningChart\footnote{The fastest C\# framework for visualisation of scientific data} and I am very excited with the visualisation of scientific data and simulation of physical processes. To my mind, studying at MathMods would significantly improve my skills in particular fields.\\

%Ending
Please, consider me as a potential candidate to Erasmus Mundus Joint Master Degree (EMJMD) programme in Mathematical Modelling in Engineering: Theory, Numerics, Applications. I beleive that this programme will have a great value in my career prospects. This experience will be a huge motivation for me to bring new ideas to the industry. \\\\


Thank you in advance.\\
Yours faithfully,\\
Alexey Tukalo
    

\end{document}
