\documentclass[english]{article}

\usepackage{babel}
\usepackage{graphicx}
\usepackage{times}
\usepackage{pifont}
\usepackage[margin=1in]{geometry}
\usepackage{eurosym}
\usepackage{fancyhdr}
\usepackage[hidelinks]{hyperref}
\pagestyle{fancy}
\fancyhf{}


%HEADER
%**************************************************************************************
\pagestyle{fancy}
\fancyhf{}
%**************************************************************************************
\lhead{Motivation Letter}
\rhead{\today}		 	 
%**************************************************************************************

\date{}
\setlength\parindent{0pt}

\begin{document}

\begin{flushright}
Alexey Tukalo,\\
airtucha@icloud.com,\\
Taivaanpankontie 14 A 14/1,\\
70200 Kuopio, Finland
\end{flushright}

Dear Madam, Sir,\\ 

Graduating from Bachelor of Information Technology I am looking for an opportunity to continue my education at Master level from the next Autumn. With this letter I hereby wish to state my interest and apply for Erasmus Mundus Joint Master Degree (EMJMD) programme in European Master on Advanced Robotics.\\

My passion to the Information Technology started at school. There I was inspired to pay a lot of extra care to the subject and as a result, I got the highest grade at the final exam of Information Technology in the history of my school. That was the reason of applying for Bachelor Degree in Information Technology in Finland. Savonia University of Applied Science provided me with an opportunity to improve my understanding of hardware as well as helped me to get a deep understanding of programming. Savonia's curriculum is very reach in terms of signal processing, electronics and different sensors technologies. So, in my point of view it gives me a strong background for a future career in field of robotics.\\

I believe that a studying at EMARO+ will help me to evolve my professional abilities to the next level. I am very impressed by the mobility structure of the programm, because it is an amazing chance to meet a lot of people with totally different cultural backgrounds, lifestyles and habits. In my point of view every person which I meet during my life can teach me something useful. So, I think that it is a great opportunity to spread the network of acquaintances and to absorb some of habits and customs of the host nations.\\

It is worth mentioning that my hobby is a landscape, street and portrait photography\footnote{500px.com/alexeytukalo}, that’s why I am especially impressed by the program, it would give me a possibility to take a large number of photos of new people from a various number of places around Europe.\\

In my opinion, this kind of travel can be an interesting challenge. However, I am sure I am able to handle it, since I have a sufficient experience of studying and working abroad. I think that it gives me an extra ability in terms of adaptation at new place. I was born in a small town located on the seashore of the White Sea at North West part of Russia. My hometown is very small, so I had to leave it to continue my education. Almost four years ago, when I was eighteen years old I moved abroad to get the world-class education. Moreover, at my third year in the University, I took part in an Erasmus+ Exchange programm in Ireland for one semester. And right after that I was hired by Karlsruhe Institute of Technology as an intern where I worked at Institute of Data Processing and Electronics for more than 4 months. The experience of data visualisation and digital image processing gained in Germany has contributed to get a part time job at Arction Oy, Finland. I hope that my skills in digital image processing will be especially useful in studying of computer vision technics and it makes the specialisation the most interesting one at the program.\\

%Ending
Please, consider me as a potential candidate to Erasmus Mundus Joint Master Degree (EMJMD) programme in European Master on Advanced Robotics. I believe that this programme will have a great value in my career prospects. This experience will be a huge motivation for me to bring new ideas to the industry.\\\\


Thank you in advance.\\
Yours faithfully,\\
Alexey Tukalo
    

\end{document}
