\documentclass[english]{article}

\usepackage{babel}
\usepackage{graphicx}
\usepackage{times}
\usepackage{pifont}
\usepackage[margin=1in]{geometry}
\usepackage{eurosym}
\usepackage{fancyhdr}
\usepackage[hidelinks]{hyperref}
\pagestyle{fancy}
\fancyhf{}


%HEADER
%**************************************************************************************
\pagestyle{fancy}
\fancyhf{}
%**************************************************************************************
\lhead{Cover Letter}		 	 
\cfoot{\thepage}
%**************************************************************************************

\date{}
\setlength\parindent{0pt}

\begin{document}

\begin{flushright}
Alexey Tukalo,\\
alexey.a.tukalo@edu.savonia.fi,\\
Taivaanpankontie 14 A 14/1,\\
70200 Kuopio, Finland
\end{flushright}

%MAIN CONTENT ******************************************************************************************************************
Dear Madam, Sir,\\\\
%intro
Hello, I am a student of Savonia University of Applied Sciences, my field of studying is an Information Technologies.\\\\
My bachelor degree program include summer internships and now I am looking for a place for this summer. \\\\
I am interested in GUI development (Java swing GUI and Android Dev. on Java). Also I have had an experience in SQL databases (Postgres SQL and Microsoft SQL Server), digital signal processing, artificial intelligent for game development, control engineering and I also has a lot of information about sensors and telecommunication in my curriculum. \\\\
I took part in an exchange program Erasmus+ and next part of the studying year I am going to spend in Institute of Technology in Tralee, Ireland. I will learn Project Management, System Architecture, Game Mechanics(Game Development with Unity3D and C\#) and Big Data. I also will have an opportunity to improve my English in the surrounding of native speakers. 
 \\\\
My hobby is photography(my photos vk.com/airphotos) and raster / vector graphics. \\\\
I would be happy if you have any available opportunity for me to have the internship.\\\\

\begin{flushright}

Best regards, Tukalo Alexey, \\EFA12SF, Savonia UAS,\\
Thanks.     

\end{flushright}

\today
\end{document}
