\documentclass[english]{article}

\usepackage{babel}
\usepackage{graphicx}
\usepackage{times}
\usepackage{pifont}
\usepackage[margin=1in]{geometry}
\usepackage{eurosym}
\usepackage{fancyhdr}
\usepackage[hidelinks]{hyperref}
\pagestyle{fancy}
\fancyhf{}


%HEADER
%**************************************************************************************
\pagestyle{fancy}
\fancyhf{}
%**************************************************************************************
\lhead{Cover Letter}
\rhead{\today}		 	 
%**************************************************************************************

\date{}
\setlength\parindent{0pt}

\begin{document}

\begin{flushright}
Alexey Tukalo,\\
airtucha@icloud.com,\\
Taivaanpankontie 14 A 14/1,\\
70200 Kuopio, Finland
\end{flushright}

%MAIN CONTENT ******************************************************************************************************************
Dear Madam, Sir,\\\\
%intro
I am a student of Savonia UAS, Kuopio, my field of study is an Information Technologies.\\\\
My bachelor degree program include summer internships and now I am looking for it. \\\\
I am interested in GUI\footnote{JavaScript, Java Swing, Android Development} and game\footnote{Unity3D} development. Also I have had an experience in SQL databases\footnote{T-SQL, PL/SQL, Postgres SQL and MicrosoftSQL Servers}, digital signal processing, artificial intelligent for games and control engineering. My first programming language is C, so I fond of C like programming languages: C++, Java, C\# and JavaScript. Right now I am learning JavaScript's framework D3.js\footnote{Data-Driven Documents} by myself, because in future I am going to get Master Degree in Data Science and Data Visualization is one of the main fields of Data Science.\\\\
Right now, I am tacking part in Erasmus+ exchange program and this part of the studying year I am going to study at Institute of Technology Tralee, Ireland. I will learn Computer Service Management, System Architecture, Visual Communication, Big Data\footnote{R, Hadoop} and Game Mechanics\footnote{Game development on Unity3D engine}, here. I also will have an opportunity to improve my English by native speakers surrounding. \\\\
In childhood I studied Visual Art for 6 years, so I am able to draw, also I am familiar with Adobe Photoshop and Illustrator.\\\\
My hobby is photography\footnote{you can find my photos here facebook.com/airtucha} and raster / vector graphics. \\\\
I think that every person which I meet during my life can teach me something. The internship in Norway is a good chance for me to get to know a lot of new people with different from mine cultural backgrounds, habits and lifestyles. I think I will have an opportunity to learn a lot during the internship and my learning will be not only connected with field of study. For sure the internship will change my point of view a lot. It will make me more open mind person and better specialist.\\\\
In addition I find Norwegian nature and architecture really fascinating because it is totally different from the ones of Karelia\footnote{the part of Russia where I was born} and Finland\footnote{there I am studying now}. It is worth mentioning that my hobby is landscape and portrait\href{https://www.facebook.com/airtucha/media_set?set=a.1404921599747323.1073741829.100006884891507&type=3}{photography}, that is why Norway is a perfect place for taking beautiful pictures of beautiful people. I have already been in Trondheim couple of years ago as tourist and I would be happy to have my internship at so amazing place.\\\\
%about friends
I really want to apply for this position because I like the description, I think it fits me well, because you are looking for mobile developer's role and it is actually satisfy my interest for GUI development. In addition I really like JavaScript and I noticed that it is one of the requirements, so it means that probably you are working with PhoneGap or something similar, unfortunately I don't have an experience with this library, but I studied Android Development with Java and I want learn PhoneGap, but I don't have enough time or susceptible project.\\\\
Thank you for spending your time and reading my cover letter.\\\\

%In attachment you can find more detailed information about me in my CV.\\\\

\begin{flushright}

     

\end{flushright}


\end{document}
