\documentclass[english]{article}

\usepackage{babel}
\usepackage{graphicx}
\usepackage{times}
\usepackage{pifont}
\usepackage[margin=1in]{geometry}
\usepackage{eurosym}
\usepackage{fancyhdr}
\usepackage[hidelinks]{hyperref}
\usepackage{float}

\pagestyle{fancy}
\fancyhf{}


%HEADER
%**************************************************************************************
\pagestyle{fancy}
\fancyhf{}
%**************************************************************************************
\lhead{Report}		 	 
\rhead{Pricelizer} 
\lfoot{\today}
\cfoot{\thepage}
\rfoot{Alexey Tukalo}
%**************************************************************************************

\date{}
\setlength\parindent{0pt}

\begin{document}

\title{\vspace{3in}Report\\
\small Pricelizer\\
}

\nopagebreak
\maketitle


\vspace{4in}



\date{\today}
\thispagestyle{empty}

\newpage
\setcounter{page}{1}
\setcounter{tocdepth}{2}

\newpage

%MAIN CONTENT ******************************************************************************************************************

\section{Introduction}
I am Alexey Tukalo, I was born in Russia, now I am studying at Savonia UAS, Kuopio, Finland. I am studying information technologies. I am interested in front-end development with JavaScript(jQuery,d3.js), HTML and CSS(Bootstrap). JavaScript is my favourite language, so I also know a little bit of Node.js. I started an internship in Pricelizer as BigData developer, but because there is no development at this filed right now I am working under front-end.\\

My strong sides are responsibility and ability to learn things quick.\\

My weak side is that I am not very skilful developer, so I am not able to create an architecture of whole project by myself and I feel myself more confident when there is somebody who can lead me and gives me tasks.\\

I also have some basic skills in design, I have got Photoshop License and I am also able to work with Illustator if it would provided to me.

\section{Done work}

I have created two static webpages, they are very rough and they were made only for testing. You can get access to them \href{https://drive.google.com/drive/folders/0B31OvwH-VznzWEhQaS1kZ1czY2M/0B71tfQ9yZsMGfktUX3hBYk1hMGZJS1ZyLTBjUERxNHdOajEyakJVVjc2TEtHbFUwVjZucGs}{here}. I also created dev.revalizer.com and tried to set the webpage for this domen, but did not find the way.

\section{My point of view}

To be honest, in my opinion the project has a lot of problems. First of all we need the graphical elements and supplies to make the page, because for example I cut the images from design layout for my testing page. We also need skilful developer who is able to create the architecture and separate the tasks between team-mates, probably he should be our back-end developer. We also need more accurate requirements and tasks, because only Karl knows how the site has to work and we can not decided it by ourselves. Sometimes it seems to be that everybody forgot that we are just interns, we are not senior developer or even juniors.



\end{document}
